Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-17 article.tex
modfis

\begin{table}[tbh]
\centering
\caption{TODO}
\begin{tabular}{@{}l *{8}{c}@{}}
\toprule
  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
\cmidrule(r){2-5}\cmidrule(r){6-9}
Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
\midrule

Directivity \textcolor{red}{appendix?} & 0.535 & 0.526 & 0.533 & 0.535 & 0.012 & 0.012 & 0.012 & 0.012 \\
Correlation            & 0.886 & 0.884 & 0.891 & 0.877 & 0.153 & 0.145 & 0.170 & 0.132 \\
GENIE3 (depth = 1)     & 0.878 & & & & 0.184 & & & \\
GENIE3 (depth = 2)     & 0.889 & & & & 0.217 & & & \\
GENIE3 (depth = 3)     & & & & & & & & \\
GTE                    & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142 \\
Partial correlation    & 0.930 &  0.927 &  0.926 &  0.923& 0.363  & 0.347 &  0.346 & 0.328 \\
Partial correlation (opt.) & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344 \\
Our approach (opt. \& avg.)    & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388 \\
Our approach + dir  \textcolor{red}{appendix?}   & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389 \\
\bottomrule
\end{tabular}
\label{tab:tab1}
\end{table}

\begin{table}[tbh]
\centering
\caption{TODO}
\begin{tabular}{@{}l *{8}{c}@{}}
\toprule
  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
\cmidrule(r){2-5}\cmidrule(r){6-9}
Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
\midrule
No  filtering       & 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
P                   & 0.925 & 0.925 & 0.924 & 0.923 & 0.322 & 0.324 & 0.323 & 0.312\\
P + W               & 0.931 & 0.930 & 0.928 & 0.927 & 0.333 & 0.334 & 0.327 & 0.313\\
P + W + PCA         & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344\\
Averaging           & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
Averaging + Directivity & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\small
\centering
\begin{tabular}{@{}l *{8}{c}@{}}
  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
\cmidrule(r){2-5}\cmidrule(r){6-9}
Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
\hline \hline
% Directivity \textcolor{red}{appendix?} & 0.535 & 0.526 & 0.533 & 0.535 & 0.012 & 0.012 & 0.012 & 0.012 \\
Correlation            & 0.886 & 0.884 & 0.891 & 0.877 & 0.153 & 0.145 & 0.170 & 0.132 \\
GENIE3 (depth = 1)     & 0.878 & & & & 0.184 & & & \\
GENIE3 (depth = 2)     & 0.889 & & & & 0.217 & & & \\
GENIE3 (depth = 3)     & & & & & & & & \\
GTE                    & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142 \\
Partial correlation    & 0.930 &  0.927 &  0.926 &  0.923& 0.363  & 0.347 &  0.346 & 0.328 \\
Partial correlation (opt.) & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344 \\
Our approach (opt. \& avg.)    & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388 \\
% Our approach + dir  \textcolor{red}{appendix?}   & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389 \\
\end{tabular}
\label{tab:tab1}
\caption{TODO}
\end{table}

\begin{table}[tbh]
\centering
\caption{TODO}
\begin{tabular}{@{}l *{8}{c}@{}}
  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
\cmidrule(r){2-5}\cmidrule(r){6-9}
Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
\midrule
No  filtering       & 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
P                   & 0.925 & 0.925 & 0.924 & 0.923 & 0.322 & 0.324 & 0.323 & 0.312\\
P + W               & 0.931 & 0.930 & 0.928 & 0.927 & 0.333 & 0.334 & 0.327 & 0.313\\
P + W + PCA         & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344\\
Averaging           & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
Averaging + Directivity & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389\\
\end{tabular}
\end{table}
